---
title: "ICC Cricket World Cup"
author: "Anup Savant"
date: "11/22/2019"
output: html_document
---

```{r}
library(readxl)
batsmen <- read_excel("C://Users//anups//Desktop//Anup//batsmen.xlsx")
batsmen
```
```{r}
## Top 10 Batsmen who has most runs in ICC Cricket World Cup

library(ggplot2)
batsmen %>%
group_by(Player) %>%
  summarize(Runs = sum(Runs))%>%
  top_n(n = 10,wt = Runs)%>%
  ggplot(aes(x = reorder(Player,Runs),y = Runs,fill = Player))+
  geom_bar(stat = "identity",show.legend = FALSE)+
  coord_flip()+
  labs(x = "Player", y ="Runs", title = "Top 10 batsman with most runs in ICC Cricket World Cup")+
  geom_text(aes(label = Runs),hjust = 1.25)
```
```{r}
library(readxl)
bowler <- read_excel("C:/Users/anups/Desktop/Anup/bowler.xlsx")
bowler
```
```{r}
## Top 5 leading wicket takers in ICC Cricket World Cup
require(tidyverse)
bowler
group_by(Player)%>%
  summarise(Wickets =  sum(`Five wicket haul`%in% Wickets))%>%
  arrange(desc(Wickets))%>%
  top_n(5)%>%
  ggplot(aes(x= reorder(Player, Wickets), y = Wickets, fill = Player))+
  geom_bar(stat = "identity",show.legend =  FALSE)+
  labs(x = "Player" , y = "Wickets", title = "Top five leading wicket takers in ICC Cricket World Cup")+
  theme(axis.text.x = element_text(angle = 100, hjust = 1.25))+
  geom_text(aes(label = Wickets, vjust =1.25))

```
```
```{r}
library(readxl)
matches <- read_excel("C:/Users/anups/Desktop/Anup/Matches Dataset.xlsx")
matches
```
```{r}
## Matches won by each team
matches%>%
  group_by(winner)%>%
  summarize(most_win = n())%>%
ggplot(aes(x = winner,y = most_win,fill = winner))+
  geom_bar(stat = "identity")+
  coord_flip()+
  scale_y_continuous("Matches won")
```

#% MOST VICTORIES BY RUNS
```{r}
require(tidyverse)
require(tidyr)
  matches %>% filter(win_by_runs == max(win_by_runs))%>%
  select(winner,win_by_runs)
```

```{r}
## MOST VICTORIES BY WICKETS
matches%>% 
  filter(win_by_wickets == max(win_by_wickets))%>%
  select(winner,win_by_wickets)
```
```{r}
#CLOSEST MARGIN VICTORY (minimum runs)
matches%>%
  filter(win_by_runs != 1)%>%
  filter(win_by_runs == min(win_by_runs)) %>%
  select(winner, win_by_runs,edition)%>%
  ggplot(aes(winner,fill = edition))+
  geom_bar()+
  coord_flip()+
  scale_y_continuous("count of win")
```
```{r}
## CLOSEST MARGIN VICTORY by Wickets
matches%>%
  filter(win_by_wickets >= 6)%>%
  filter(win_by_wickets == min(win_by_wickets))%>%
  select(winner,win_by_runs,edition)%>%
  ggplot(aes(winner, fill = edition))+
  geom_bar()+
  coord_flip()+
  scale_y_continuous("Wickets")
```
```{r}
#MOST SUCCESSFUL TEAMS
matches %>% 
  group_by(winner, edition)%>%
  summarize(most_win = n())%>%
  filter(most_win == max(most_win)) %>% arrange(desc(edition,most_win))
```

```{r}
matches
mean(matches$win_by_runs, na.rm = T)
mean(matches$win_by_wickets, na.rm = T)
median(matches$win_by_wickets, na.rm = T)
hist(matches$win_by_wickets)

## Histogram win by wickets and win by runs is rightly skewed and is positively skewed.
```



```{r}
require(lattice)

``
```{r}
batsmen
```

```
## Predicitive Analysis

```{r}
require(lattice)
```

`
```
```{r}
## Model 4 : Batting Form in world cups

require(tidyverse)
batsmen
cor(batsmen$Mat, batsmen$Runs)
```

```{r}
require(lattice)
batsmen
xyplot(Runs~ Mat, data = batsmen)

```

```{r}
summary(lm(Runs~Mat , data = batsmen))

```

```{r}
ggplot(data = batsmen, aes(x = Mat, y = Runs)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)

```

```

```{r}
library(readxl)
bowler <- read_excel("C://Users//anups//Desktop////bowler.xlsx")
bowler
```
```
```{r}
library(readxl)
bowler <- read_excel("C://Users//anups//Desktop//Anup//bowler.xlsx")
bowler
```

```{r}
## Model 1 : Bowling form in world cups.
bowler
xyplot(Overs ~ Runs, data = bowler)
```
`
Model 3: Bowler Form
```{r}
## Correlation coefficent
require(tidyverse)
bowler
cor(bowler$Runs, bowler$Overs)
```


```{r}
bowler
summary(lm(Overs ~ Runs, data = bowler))
```

```

```{r}
ggplot(data = bowler, aes(x = Overs, y = Runs)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
batsmen
```

## Model 2: Consistent Batsmen
```{r}
## Correlation coefficient 
cor(batsmen$Runs, batsmen$Inns)
```

```{r}

xyplot(Inns ~ Runs, data = batsmen)
```

```{r}
summary(lm(Inns ~ Runs , data = batsmen))
```


```{r}
ggplot(data = batsmen, aes(x = Runs, y = Inns)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
```
```{r}
bowler
```
```{r}
#Consistent bowler in World Cups

xyplot(Runs ~ Wickets, data = bowler)
```

## Model 1 : Consistent Bowler
```{r}
## Correlation Coefficeint
cor(bowler$Runs, bowler$Wickets)

```

```{r}
summary(lm(Runs ~ Wickets, data = bowler))
```

```{r}
ggplot(data = bowler, aes(x = Runs, y = Wickets)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
require(tidyverse)
bowler = bowler %>% mutate( Average = as.numeric(Ave), SR = Overs/Wickets)
bowler

bowler %>% mutate(bowling_form = 0.3269*Overs + 0.2846*Inns + 0.1210*Average +0.1877*SR + 0.0798*`Five wicket haul`) %>% arrange(bowling_form)
```

```{r}
require(tidyverse)
bowler = bowler %>% mutate( Average = as.numeric(Ave), SR = Overs/Wickets)
bowler

bowler = bowler %>% mutate(bowling_consistency = 0.4174*Overs + 0.2634*Inns + 0.1602*SR +0.0975*Average + 0.0615*`Five wicket haul`) %>% arrange(bowling_consistency)
```


